Making Sequential Programs Deterministic

### 2019-04-06 java-design.tex
Edits in case study and java-design
java design typos

Just as a qualifier variable $\kappa$ is written as \<@PolyDet> in Java
source code, $\up{\kappa}$ is written as \<@PolyDet("up")>, and
$\down{\kappa}$ is written as \<@PolyDet("down")>.  An occurrence of a
qualifier variable that does not affect the binding of that variable
(\cref{bindings-uses}) is written \<@PolyDet("use")>.

@@

>>>>

Just as a qualifier variable $\kappa$ is written as \<@PolyDet> in Java
source code, $\up{\kappa}$ is written as \<@PolyDet("up")>, and
$\down{\kappa}$ is written as \<@PolyDet("down")>.  An occurrence of a
qualifier variable that does not affect the binding of that variable
($\use{\kappa}$ in \cref{bindings-uses}) is written \<@PolyDet("use")>.

@@

Although \theDeterminismChecker performs local type inference within method bodies,
it does not perform whole-program type inference.
This makes separate compilation possible.
It forces programmers to write specifications (type qualifiers) on methods,
which is good style and valuable documentation.
